I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-12 Paper/Paper_noProof.tex
ALGO

>>>>

\SetKwInput{KwInput}{Input}
\SetKwInput{KwOutput}{Output}

\begin{algorithm}[t!]
	\caption{}
	\label{algo1}
	\KwInput{Bounds $[\alpha_n,\beta_n]$ for input nodes $n$ at layer $0$}

	\KwOutput{Bounds $[\alpha_n,\beta_n]$ for every node $n$}

	 Run DeepPoly to obtain preliminary lower and upper bounds for all nodes.

	 Precompute $\mathcal{R}$ to know the compensation strenght

	 \For{layer $k=1 \cdots \ell$}{

	 \If{$k$ = 0}{

	 $\mathcal{D}$, $\boldsymbol{W}, \boldsymbol{b}$ $\rightarrow$ $\mathcal{B}_0$ = \{$x$: $(UB(x),LB(x))$,$\cdots$\}

	 \tcp*{Do linear transformation  from input to the first layer}

	 \For{$x$ in $Nodes_l$}{

	 $x$, $\mathcal{B}$, $\mathcal{R}$  $\rightarrow$ $\mathcal{O}$ \tcp*{To get the open node list $\mathcal{O}$}

}
}	
}	
	\Return{$\mathcal{B}$}	
	\end{algorithm}
